%______________________________________________________________________________________________________________________
% @brief    LaTeX2e Resume for Kevin T. Manley
\documentclass[margin,line]{resume}


%______________________________________________________________________________________________________________________
\begin{document}
\name{\Large Kevin T. Manley}
\begin{resume}

    %__________________________________________________________________________________________________________________
    % Contact Information
    \section{\mysidestyle Contact\\Information}

    20 Clayton Place			                            \hfill kevin.manley@gmail.com       \vspace{0mm}\\\vspace{0mm}%
    Ridgefield, CT 06877                                    \hfill linkedin.com/in/kevinmanley        \vspace{0mm}\\\vspace{0mm}%
    mobile: +1 203 501 5006 					\hfill github.com/kmanley  \vspace{0mm}\\\vspace{-4.5mm}%


    %__________________________________________________________________________________________________________________
    % Profile 
    \section{\mysidestyle Profile}

    Full stack developer. Hands-on software architect. Excellent communicator. Effective as individual contributor or team leader.
    
    %__________________________________________________________________________________________________________________
    % Professional Experience
    \section{\mysidestyle Professional\\Experience}

    \textbf{Utiliz (myutiliz.com)}, Ridgefield, CT\\
    \textsl{Founder \& CTO} \hfill \textbf{Apr 2016 -- Present}\\
    Built all company technology: consumer site, admin site, simulation \& workflow engine, web scrapers, supplier \& payment integration.
    Go/RethinkDB/HTML/jQuery/AWS (S3, SES)/Stripe.

    \textbf{Bank of America Merrill Lynch}, New York, NY\\
    \textsl{Director} \hfill \textbf{Jun 2012 -- Dec 2015}\\
    Built trading \& marking applications for multi-billion dollar mortgage trading desk. Managed a 
    global team. Python/NoSQL/grid/async/GUI.
         
    \textbf{Bridgewater Associates}, Westport, CT\\
    \textsl{Software Architect} \hfill \textbf{Aug 2010 -- Jun 2012}\\
    Built backoffice app framework for world's largest hedge fund. Brought modern ideas to an aging software stack, improving
    performance \& reliability. Trained and mentored team. Python/C\#/SQL Server/HTML/jQuery/REST. 

	\textbf{Independent Consultant}, London, UK \hfill \textbf{Jul 2006 -- Aug 2010}\\
    Specialized in scaling hedge fund and bank EOD batch processing using grid computing.\\
    Python/C/C++/SWIG/SQL Server/HTML/Javascript/Sungard Front Arena/grid/async.
    \vspace{0mm}

    \begin{description}
    \item[$\cdot$ Standard Bank] Built next generation credit risk engine, result was 50\% less code and 5x faster. 
    \item[$\cdot$ Capula Global] Leveraged unused capacity on 70 desktop machines to speed up EOD batch 4x.
    \item[$\cdot$ Conduit Capital] Built a fast, distributed Monte Carlo pricing framework for exotic derivatives.
    \item[$\cdot$ Peloton Partners] Sped up daily P\&L reporting 14x from 7h to 30m.
    \item[$\cdot$ Citi] Implemented cost-based distributed FX option pricing on Platform Symphony grid.   
    \item[$\cdot$ Barclays Capital] Key developer on Core Risk Engine. Embedded Python for easier testing.
    \end{description}    

    \textbf{Arts Alliance Media Ltd.}, London, UK\\
    \textsl{Architect \& Lead Software Developer} \hfill \textbf{Oct 2002 -- Jun 2006}\\
	Built Newman Online, an advanced SaaS cinema management system currently running hundreds of screens across Europe.
    Python/SQL Server/XML/HTML/electronic payments/hardware integration.

    \textbf{Software Developer}, Tucson, AZ \& Seattle, WA \hfill \textbf{Sep 1992 -- Oct 2002}\\
	Multiple C/C++ roles from mobile games to Internet ad servers. Details on request. 
	
    \textbf{US Air Force}, Davis-Monthan Air Force Base, Tucson, AZ\\
    \textsl{Officer} \hfill \textbf{Sep 1988 -- Sep 1992}\\
    Transformed the bio-engineering field with novel software. Led a team in Operation Desert Storm.
	
    %\vspace{5cm}
    %__________________________________________________________________________________________________________________
    % Computer Skills
    \section{\mysidestyle Programming\\Skills} 

    Python, Go (golang), HTML, CSS, JS/jQuery, C/C++, SQL, NoSQL, concurrent/async/event-driven programming, grid computing, 
    SOA, microservices, OOP, XML, JSON, HTTP, REST, TCP/IP, requirements gathering, large scale software design, TDD,  
    Agile, version control (git, svn)

    %__________________________________________________________________________________________________________________
    % Education
    \section{\mysidestyle Education}
	%\textbf{7City}, London, United Kingdom. \hfill \textbf{2011--Present}\\
	%\vspace{0mm}\\\vspace{0mm}%
	%\textsl{Certificate in Quantitative Finance (In progress)}\\
	\textbf{University of Washington}, Seattle, WA \hfill \textbf{2001--2002}\\
	%\vspace{0mm}\\\vspace{0mm}%
	\textsl{MS Computer Science (Honors)} \\
	\textbf{Worcester Polytechnic Institute}, Worcester, MA \hfill \textbf{1984--1988}\\
	%)\vspace{0mm}\\\vspace{0mm}%
	\textsl{BS Electrical Engineering (High Distinction)}. 4 Year US Air Force Scholarship. 
    
    %__________________________________________________________________________________________________________________
    % Referees
    \section{\mysidestyle References} 
    {\sl Available on request}

%______________________________________________________________________________________________________________________
\end{resume}
\end{document}

%______________________________________________________________________________________________________________________
% EOF

